%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------


\documentclass[preprint, 10pt]{sigplanconf}

% The following \documentclass options may be useful:
%
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% authoryear    To obtain author/year citation style instead of numeric.

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{array}
%\usepackage{algorithmic}
%\usepackage{algorithm}
\usepackage{textcomp}
\usepackage{listings}
%\usepackage{hyperref}
\begin{document}

\conferenceinfo{SPLASH '11}{date, City.}
\copyrightyear{2011}
\copyrightdata{[to be supplied]}

\titlebanner{Crossfire Debugging Protocol}        % These are ignored unless
\preprintfooter{Crossfire - Multiprocess, Cross-Browser, Open-Web Debugging Protocol}   % 'preprint' option specified.

\title{Crossfire - Multiprocess, Cross-Browser, Open-Web Debugging Protocol}


\authorinfo{Michael G. Collins}
           {IBM Research - Almaden}
           {mgcollin@us.ibm.com}
\authorinfo{John J. Barton}
           {IBM Research - Almaden}
           {bartonjj@us.ibm.com}

\maketitle

\input{abstract.tex}

\category{CR-number}{subcategory}{third-level}

\terms
term1, term2

\keywords
keyword1, keyword2

\input{introduction.tex}
\input{jjb.tex}
%\input{design.tex}
\input{protocol.tex}
\input{implementation.tex}
\input{relatedwork.tex}
\input{futurework.tex}
\input{conclusion.tex}

%\appendix
%\section{Appendix Title}

%This is the text of the appendix, if you need one. I don't

\acks
As a multi-year open source effort, \textit{Crossfire} results from a broad collaboration and 
contributions from many individuals. Simon Kaegi from the Orion team lead us towards collaboration with the Orion and Eclipse teams. Darin Wright wrote the initial implementation of the Tools Interface. Grant Gayed and Mike Rennie heavily influenced the \textit{Crossfire} protocol during their implementation of the IE server and Eclipse clients. Pedro Simonetti Garcia, Kevin Dangoor, and Atul Varma provided key insights to the module loading work. Jan 'Honza' Odvarko powers the Firebug project essential to our evolution strategy, especially implementing a test suite critical to maintaining the quality of the waypoint implementations. Steven Roussey helped with an early implementation and feedback on issues it raised.


% We recommend abbrvnat bibliography style.

\bibliographystyle{abbrvnat}
\bibliography{bibliography}

% The bibliography should be embedded for final submission.

%\begin{thebibliography}{}
%

%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
%P. Q. Smith, and X. Y. Jones. ...reference text...


\end{document}
