
\section{Introduction}
Web Applications continue to grow in size and complexity. Asynchronous background 
data download (AJAX) started the surge. 
This led to the 
emergence of common toolkits and libraries for Javascript which drove  performance
increases in Web Browsers fueling more growth in client-side Web application
development. These improvements, combined with new features available in Web browsers 
shifted investment from server- to client-side. Recent empirical analysis of representative
 major Web sites shows program sizes in the range of hundreds of kilobytes of
sophisticated code.\cite{VitekDynamicJS2010}

To develop and maintain these large applications, programmers and designers rely on 
numerous tools, most notably Web page debuggers. 
This paper describes a major re-architecting of the most widely used Web page debugger, 
Firebug, as a client/server system and in particular the 
\textit{Crossfire} protocol designed to support its client-server communications.  
Our description focuses on practical, state-of-the-art issues in an on-going and fast-moving project. 
Thus we cover details of protocol important for implementation and issues of 
matching resources to goals important for project management: we must deal with both 
extremes to succeed.

\section{Background}
To understand the importance and challenges of the \textit{Crossfire} work we start by introducing Firebug.
Released by Joe Hewitt in 2006, Firebug was the first integrated Web debugger. Firebug is a runtime 
debugger: it directly accesses, responds to, and operates on the running Web browser.  Rather than separate 
views of JavaScript, CSS, and HTML, Firebug integrated its views such that interaction with, 
for example, an HTML element would cause synchronized views of the CSS rules. Rather than static 
 views of browser state, Firebug included dynamics like network traffic analysis and console logging; rather 
than read-only views, Firebug allowed live edits where possible so developers could try out changes.
The resulting tool became very popular with developers and contributing significantly to the growth in Web applications.

The primary implementation of Firebug is a Firefox extensions, a supplemental software 
component that loads into the Firefox Web browser. A secondard implementation with fewer features and, 
in particular, limited support for JavaScript debugging, called Firebug Lite works in multiple browsers. 
The success of Firebug lead to implemenations of Web Page debuggers in other browsers, including 
DragonFly for Opera, Web Inspector for Google Chrome and Apple Safari, and the developer tool in 
Microsoft Internet Explorer. Since 2007 Firebug has been developed as an open source project, with 
seven major releases.

To give a flavor of the kinds of operations Firebug supports, we outline  an example more completely
described in Ref.\cite{jjb-www2010}. Suppose a developer wants to understand why a block of text 
in the Web page turned green while the page was loading. They might use the Firebug "inspect" feature, 
causing Firebug to display the HTML element under the mouse. They see that the element has a \textit{style}
attribute setting the color green. While hovering over the green block of text, 
the developer clicks down to lock
the user interface on the element, then moves to the HTML panel in Firebug and right clicks on the 
selected HTML element representation. A menu pops up allowing the developer to select "Break On Attribute Change". 
When the developer reloads the page, Firebug halts in the JavaScript code panel, on the line where 
the attribute is changed from red to green.

This example illustrates that we will need to synchronize mouse events on the Web page with the debugger UI,
identify HTML element representations rendered in the debugger UI with the elements in the Web page and synchronize
DOM mutation event handling wit JavaScript execution.


(Refactoring timeline)
=======
Web Applications continue to grow in size and complexity. The
emergence of common toolkits and libraries for Javascript along with performance
increases in Web Browsers fuels growth in client-side Web application
development. As more functionality shifts from server- to client-side, the size
of Javascript codebases naturally increases. Unfortunately for developers, the
tools to develop, manage, and debug larger codebases have not followed the
applications into the Web application development space.

Sophisticated development tools become crucial for understanding
and working with larger codebases. Compilers, debuggers, and other tools are
often combined to create an Integrated Development Environment (IDE) where
most, if not all, development tasks can be performed. Web development tools, on
the other hand, often reside in the Web Browser. In 2011, most Web
browsers ship with some kind of Web development tools included\cite{something},
and still more are available as plugins or add-ons. These tools operate
directly on the runtime Web application that is loaded into the browser, and do
not retain any knowledge of or connection to the original source code. Therefore
a developer must manually apply any changes made in one of these tools to his or
her source code.

This class of built-in Web development tools allow for a powerful set of
features.  However, several weaknesses.

Tools such as ``Inspectors'' and Firebug's HTML Breakpoints\cite{jjb-www2010}
enable developers to quickly locate the section of code they are interested in.

The rise of Mobile and Tablet computers which ship with fully functional Web
browsers means that Web application developers have additional form-factors to
consider.

Tools such as ``Inspectors'' and Firebug's HTML Breakpoints\cite{jjb-www2010}
enable developers to quickly locate the section of code they are interested in.

Crossfire is designed to support the features available in current built-in
development tools such as Firebug, while enabling the advantages of a remote
debug connection.


