%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------


\documentclass[10pt]{sigplanconf}

% The following \documentclass options may be useful:
%
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% authoryear    To obtain author/year citation style instead of numeric.

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{array}
%\usepackage{algorithmic}
%\usepackage{algorithm}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{url}
\usepackage{breakurl}
\begin{document}

%\conferenceinfo{SPLASH '11}{date, City.}
%\copyrightyear{2011}
%\copyrightdata{[to be supplied]}

\conferenceinfo{SPLASH'11 Companion,} {October 22--27, 2011, Portland, Oregon,
USA.}
\CopyrightYear{2011}
\copyrightdata{978-1-4503-0942-4/11/10}

\titlebanner{Crossfire Debugging Protocol}        % These are ignored unless
\preprintfooter{Crossfire - Multiprocess, Cross-Browser, Open-Web Debugging Protocol}   % 'preprint' option specified.

\title{Crossfire - Multiprocess, Cross-Browser, Open-Web Debugging Protocol}


\authorinfo{Michael G. Collins}
           {IBM Research - Almaden}
           {mcollins@collinsmichaelg.com}
\authorinfo{John J. Barton}
           {IBM Research - Almaden}
           {johnjbarton@johnjbarton.com}

\maketitle

%\input{abstract.tex}
\begin{abstract}
We present \textit{Crossfire}, a system and protocol designed to enable
debugging of Web pages in another process or machine. Issues specific to any one
Web browser are abstracted by the protocol and implementation,
allowing a new generation of Open Web development tools to be implemented. We discuss the major refactoring of Firebug, the open source Web debugging tool
to use \textit{Crossfire} and the interplay between goals and resources that such an effort requires.
In addition to the cross-browser focus of the protocol, we also discuss support for extensions which themselves will be
cross-browser and client-server.
\end{abstract}

\category{  D.2.5}{Software Engineering}{Testing and Debugging— debugging aids, distributed debugging}


\terms
Experimentation, Reliability

\keywords
Source-Level Debugging, Distributed Debugging, Open Source

\input{introduction.tex}
\input{design.tex}
\input{protocol.tex}
\input{implementation.tex}
\input{relatedwork.tex}
\input{futurework.tex}
\input{conclusion.tex}


\acks
As a multi-year open source effort, \textit{Crossfire} results from a broad collaboration and
contributions from many individuals. Simon Kaegi from the Orion team lead us towards collaboration with the Orion and Eclipse teams. Darin Wright wrote the initial implementation of the Tools Interface. Grant Gayed and Mike Rennie heavily influenced the \textit{Crossfire} protocol during their implementation of the IE server and Eclipse clients. Pedro Simonetti Garcia, Kevin Dangoor, and Atul Varma provided key insights to the module loading work. Jan 'Honza' Odvarko powers the Firebug project essential to our evolution strategy, especially implementing a test suite critical to maintaining the quality of the waypoint implementations. Steven Roussey helped with an early implementation and feedback on issues it raised.


% We recommend abbrvnat bibliography style.

\bibliographystyle{abbrvnat}

%\bibliography{bibliography}

% The bibliography should be embedded for final submission.

\begin{thebibliography}{27}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[web(2001)]{websocketapi}
Web{S}ocket {API} {S}pecification, 2001.
\newblock \url{http://dev.w3.org/html5/websockets/}.

\bibitem[jdw(2004)]{jdwp}
\emph{Java {P}latform {D}ebugger {A}rchitecture}, 2004.
\newblock \url{http://download.oracle.com/javase/1.5.0/docs/guide/jpda/}.

\bibitem[gdb(2007)]{gdb-song}
{GDB} {S}ong, 2007.
\newblock \url{http://www.gnu.org/music/gdb-song.html}.

\bibitem[chr(2009)]{chrome-dev-tools}
Google {C}hrome {D}ev {T}ools {P}rotocol, 2009.
\newblock
  \url{http://code.google.com/p/chromedevtools/wiki/ChromeDevToolsProtocol}.

\bibitem[Web(2010)]{WebInspector}
Web{K}it {W}eb {I}nspector, 2010.
\newblock \url{http://trac.webkit.org/wiki/WebInspector}.

\bibitem[clo(2010)]{cloud9}
Cloud 9, 2010.
\newblock \url{http://cloud9ide.com/}.

\bibitem[gdb(2010)]{gdb-rsp}
\emph{{GNU} {D}ebugger ({GDB}) {M}anual}, 2010.
\newblock \url{http://sourceware.org/gdb/current/onlinedocs/gdb/}.

\bibitem[ope(2010)]{opera-scope}
Opera {S}cope {P}rotocol, 2010.
\newblock \url{http://dragonfly.opera.com/app/scope-interface/}.

\bibitem[web(2010)]{websocketprotocol}
Web{S}ocket {P}rotocol, 2010.
\newblock \url{http://www.whatwg.org/specs/web-socket-protocol/}.

\bibitem[Ecl(2011)]{EclipseJSDT}
Eclipse {JSDT}, 2011.
\newblock \url{http://wiki.eclipse.org/JSDT/Debug}.

\bibitem[Goo(2011)]{GoogleChrome}
Google {C}hrome, 2011.
\newblock \url{http://www.google.com/chrome}.

\bibitem[IET(2011)]{IETools}
Microsoft {I}nternet {Explorer} {D}eveloper {T}ools, 2011.
\newblock \protect\url{http://msdn.microsoft.com/en-us/library/dd565628}.

\bibitem[V8(2011)]{V8}
V8 {D}ebug {P}rotocol, 2011.
\newblock \url{http://code.google.com/p/v8/wiki/DebuggerProtocol}.

\bibitem[com(2011)]{commonjs}
Common{JS}, 2011.
\newblock \url{http://www.commonjs.org/}.

\bibitem[cro(2011{\natexlab{a}})]{crossfire-doc}
Crossfire online documentation, 2011{\natexlab{a}}.
\newblock \url{http://getfirebug.com/wiki/index.php/Crossfire}.

\bibitem[cro(2011{\natexlab{b}})]{crossfire-src}
Crossfire source repository, 2011{\natexlab{b}}.
\newblock \url{http://fbug.googlecode.com/svn/extensions/crossfire/branches/}.

\bibitem[fir(2011{\natexlab{a}})]{firebug-doc}
Firebug developer api documentation, 2011{\natexlab{a}}.
\newblock \url{http://getfirebug.com/developer/api/firebug1.7/}.

\bibitem[fir(2011{\natexlab{b}})]{firebug-src}
Firebug source repository, 2011{\natexlab{b}}.
\newblock \url{http://fbug.googlecode.com/svn/branches/}.

\bibitem[get(2011)]{getfirebug}
Firebug website, 2011.
\newblock \url{http://getfirebug.com}.

\bibitem[ope(2011)]{opera-dragonfly}
Opera {D}ragon{F}ly, 2011.
\newblock \url{http://www.opera.com/dragonfly/}.

\vfill\eject

\bibitem[ori(2011)]{orion}
Orion, 2011.
\newblock \url{http://www.eclipse.org/orion/}.

\bibitem[Barton and Odvarko(2010)]{jjb-www2010}
J.~J. Barton and J.~Odvarko.
\newblock Dynamic and graphical web page breakpoints.
\newblock In \emph{Proceedings of the 19th international conference on World
  wide web}, WWW '10, pages 81--90, New York, NY, USA, 2010. ACM.
\newblock ISBN 978-1-60558-799-8.
\newblock \doi{http://doi.acm.org/10.1145/1772690.1772700}.
\newblock URL \url{http://doi.acm.org/10.1145/1772690.1772700}.

\bibitem[Burke(2011)]{requirejs}
J.~Burke.
\newblock Require{JS}, 2011.
\newblock \url{http://requirejs.org/}.

\bibitem[Caraveo and Rethans(2007)]{dbgp}
S.~Caraveo and D.~Rethans.
\newblock {DBGP, A common debugger protocol for languages and debugger UI
  communication, Draft 16}, 2007.
\newblock \url{http://www.xdebug.org/docs-dbgp.php}.

\bibitem[Crockford(2006)]{json}
D.~Crockford.
\newblock {JSON}, 2006.
\newblock \url{http://json.org}.

\bibitem[Mueller(2011)]{weinre}
P.~Mueller.
\newblock Weinre, 2011.
\newblock \url{http://pmuellr.github.com/weinre/ }.

\bibitem[Richards et~al.(2010)Richards, Lebresne, Burg, and
  Vitek]{VitekDynamicJS2010}
G.~Richards, S.~Lebresne, B.~Burg, and J.~Vitek.
\newblock An analysis of the dynamic behavior of javascript programs.
\newblock In \emph{Proceedings of the 2010 ACM SIGPLAN conference on
  Programming language design and implementation}, PLDI '10, pages 1--12, New
  York, NY, USA, 2010. ACM.
\newblock ISBN 978-1-4503-0019-3.
\newblock \doi{http://doi.acm.org/10.1145/1806596.1806598}.
\newblock URL \url{http://doi.acm.org/10.1145/1806596.1806598}.

\end{thebibliography}

\end{document}
